%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Home Team Science \(\&\) Technology Agency } % Organization
    {Intern } % Job title
    {Singapore} % Location
    {Jan. 2025 - Jun 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an AI chatbot with a Retrieval-Augmented Generation (RAG) pipeline using Llama.cpp and LangChain, improving document retrieval efficiency by 30\%.}
        \item {Conducted field testing for deployed robots, ensuring robustness and seamless user transition.}
        \item {Designed and implemented a motion control library for a bipedal humanoid robot, enhancing locomotion stability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Nanyang Technological University} % Organization
    {Maker and Tinkering Lab Assistant } % Job title
    {Singapore} % Location
    {Sep. 2023 - Dec 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mentored over 50 CN Yang Scholars in electronics, CAD design, and prototyping.}
        \item {Designed and 3D-printed over 100 custom components in SOLIDWORKS for research projects.}
        \item {Developed custom PCB and Arduino shields with KiCAD, optimising performance across various applications.}
        \item {Maintained and serviced over 30 3D printers and 8 soldering stations, minimising downtime.}
        \item {Supported NTU Openhouse events and Physics lectures experiments, enhancing interactive learning experiences.}
      \end{cvitems}
    }

% ---------------------------------------------------------
  \cventry
    {Nanyang Technological University} % Organization
    {Teaching Assistant} % Job title
    {Singapore} % Location
    {Jan. 2024 - Apr 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught a Motion Study Control Class using an Ender 3 frame, Ramps 1.4 controller, Marlin firmware, and CNCjs software, mentoring a total of 32 students throughout the semester.}
        \item {Evaluated and provided constructive feedback on student assignments and projects, helping them improve their understanding and performance.}
        \item {Supported students during lab sessions, ensuring they applied theoretical concepts effectively and troubleshooting technical issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Makers Lab Assistant } % Job title
  %   {Nanyang Technological University} % Organization
  %   {Singapore} % Location
  %   {Jan. 2024 - May 2024} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market.}
  %       \item {Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic and designed game graphics.}
  %       \item {Won the 2nd prize in final evaluation.}
  %     \end{cvitems}
  %   }


%--------------------------------------------------------
  \cventry
    {Gavin's Tuition} % Organization
    {IT Manager} % Job title
    {Singapore} % Location
    {Aug. 2022 - Feb 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented smart systems across two centres, streamlining operations and improving client experience.}
        \item {Managed IT infrastructure and server maintenance, enhancing system reliability.}
        \item {Developed and launched two Python computing courses, expanding the educational offerings and boosting student enrollment.}
      \end{cvitems}
    }
    
%-%--------------------------------------------------------
%   \cventry
%     {Logistics Specialist} % Job title
%     {Singapore Armed Forces} % Organization
%     {Singapore} % Location
%     {Sep. 2020 - Jul 2022} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Implemented RESTful API server for car rental booking application(CARPLAT in Google Play).}
%         \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
%         \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------

  \cventry
    {Ngee Ann Polytechnic} % Organization
    {Software Developer} % Job title
    {Singapore} % Location
    {Jan. 2020 - Sep 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed ROS-based software for mobile bases, with a focus on enhancing navigation and operational.}
        \item {Developed Linux services to automate startup commands and enable journaling for enhanced system management.}
        % \item {Integrated IMU, camera, and odometry sensors with a Kalman filter to enhance data accuracy and system stability.}
        % \item {Documented processes in video, then uploaded them to YouTube for broader accessibility and knowledge.}
      \end{cvitems}
      \vspace{5mm}
      \begin{cvsubentries}
       \cvsubentry{}{Autonomous Mobile Base}{Jun. 2020}{}
       \begin{flushleft}
       \hspace{5mm} - Led a team of 3 in building an Autonomous Mobile Base using ROS, achieving a successful proof-of-concept.
       \end{flushleft}
       \begin{flushleft}
       \hspace{5mm} - Designed and constructed the mechanical structure, circuitry, and SLAM algorithm from the ground up, ensuring system integration.
       \end{flushleft}
       \cvsubentry{}{NParks Patrol Robot}{Mar. 2020}{}
       \begin{flushleft}
       \hspace{5mm} - Partnered with NParks to deploy a safe-distancing robot at Bukit Timah Nature Reserve, enhancing public safety.
       \end{flushleft}
       \begin{flushleft}
       \hspace{5mm} - Integrated 3D SLAM on a SCOUT base with 3D LiDAR, enabling navigation in complex and obstructed environments on uneven terrain.
       \end{flushleft}
       \begin{flushleft}
       \hspace{5mm} - Developed facial recognition and person detection software using OpenCV and PyTorch, improving real-time monitoring and compliance.
       \end{flushleft}
       \cvsubentry{}{Teaching Assistant Robot - CODDIE}{Jan. 2020}{}
       \begin{flushleft}
       \hspace{5mm} - Led the development of ROS navigation stack, and integration with latte panda for user control.
       \end{flushleft}
       \begin{flushleft}
       \hspace{5mm} - Featured in multiple media outlets including newspapers for innovative contributions to educational technology.
       \end{flushleft}
      \end{cvsubentries}
    }

% %---------------------------------------------------------
%   \cventry
%     {Makers Lab Assistant } % Job title
%     {Nanyang Technological University} % Organization
%     {Singapore} % Location
%     {Sep. 2023 - Dec 2024} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Conducted penetration testing on SAMSUNG Smart TV.}
%       \end{cvitems}
%       %\begin{cvsubentries}
%       %  \cvsubentry{}{SUBENTRY}{Sep. 2013}{}
%       %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%       %\end{cvsubentries}
%     }

% %---------------------------------------------------------
\end{cventries}
